Meta-analysis

### 2019-07-19 05_MetaAnalysis.Rmd
removed -1 As a random variable
replaced -1
addding sampling variance calculation for mung1112/02

```{r Fungicides}
unique(PM_MB_means$Fungicide)
PM_MB_means %>%
   group_by(Fungicide,Trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   kable()

@@

>>>>

```{r Fungicides}
unique(PM_MB_means$Fungicide)
PM_MB_means %>%
   group_by(Fungicide,Trial_ref) %>%
   summarise() %>%
   count(sort = T) %>%
   rename(Trials = n) %>%
   kable()

@@

```{r LSD_2_MSE}
# Formula and modifications based off information found at https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/
colnames(PM_MB_means)

Tcrit <- 1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups
DFw <- sum(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates) - 
   length(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates) # degrees of freedom within groups
n.A <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]
n.B <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[2]
LSD <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Yield_error[1]

# SSwithin <- #unknown
# MSW <- SSwithin / DFw # mean square within (SS within / DF within)

#  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
#  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B)

```
![calculating sampling variance from mean squared error Paul et. al. (2008)](Paul_etal_2008.PNG)

```{r sampling_variance}
for(j in seq_along(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates)){
   if(j == 1){Sv <- vector(length = length(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates))}
#  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[j] *
#                   PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$grain_yield.t.ha.[j])
# Balance equation 
   Sv[j] = sqrt(MSE/(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[j] *
                  as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$grain_yield.t.ha.[j])))

   }
